### 2022-06-19 paper/Chapters/Chapter01.tex
update paper

%% add noise image
\begin{figure}[!h]
	\centering
	\begin{tikzpicture}
		\node[inner sep=0pt] (depthmap) at (0,0)
		{\includegraphics[width=.6\textwidth]{./pic/00028.depth0.png}};
	\end{tikzpicture}
	\caption{A captured depth map via infrared sensors. Pixels that far away represent by light colors, otherwise by dark colors. The black dots are the depths that failed to be detected. The black dots distribute in all of the images.}
	\label{fig:depth_map_with_noise}
\end{figure}

%% add noise image
\begin{figure}[!h]
	\centering
	\begin{tikzpicture}	
		\node[inner sep=0pt] (normal) at (8,0)
		{\includegraphics[width=.6\textwidth]{./pic/00028.normal0.png}};
	\end{tikzpicture}
	\caption{Semi-dense Normal Map calculated from depth map using a standard method}
	\label{fig:standard_normal_inference}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% intro %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Introduction}
As a popular and affordable new type of depth sensor, Kinect, had attracted a great focus to computer vision research in the last decades. It simultaneously captured the grayscale or RGB image and depth map with a high resolution. The depth map can further convert to structured point clouds with known intrinsic calibration parameters, which can use in many applications.

%% why surface normal is important
Surface Normal is one of the most worthy pieces of information that can inferr from point clouds, which applies in many practical applications, such as augmented reality and robotics. Some tasks like shading and surface reconstruction require normal as one of the inputs. However, due to the lack of accuracy of the sensors, the  surface normal inference from depth maps/point clouds has many challenges.

@@

%% CNN based methods
Recently, deep learning based method \cite{yolov3}, \cite{efficientDet} achieved a great succeed for image processing. 
These network architectures use a batch of RGB/Grayscale images as input and usually employ for classification problems. Usually, the images are convoluted with a convolutional layer and downsampling with pooling layers. The outputs of the network consist of a single value to represent the index of the corresponding class \cite{efficientDet}, or with a set of values to represent the position of bounding boxes.\cite{yolov3}.

%%%%%%%%%%%%%%%%%%% talk about the chanllege of this task %%%%%%%%%%%%%%%%%%
%% talk about the reason we need a new type of network architecture
However, in many other vision tasks, like normal map inference, the output is demanded as the same shape as the input. Instead of predicting one or several classes for the whole input matrix, the class for each pixel requires for prediction. In this case, the traditional network architecture is not suitable anymore.

@@

%%%%%%%%%%%%%%%%%% talk about the main work in this thesis  %%%%%%%%%%%%%%%%%%
In this thesis, we found a solution for the problems mentioned above and proposed a novel deep learning architecture for surface normal inference. A network named Albedo Gated Normal Inference Network(AlGaN) is proposed to infer normal given the corresponding depth map. The architecture of AlGaN involves a two-stage CNN. The first stage infers the normal map using point cloud as input. If the light source position and grayscale image can be provided further, the second stage infers the albedo altogether with the normals from the first stage. In addition, the loss function is based on least-square error and Lambertian reflection.

>>>>

% Chapter Template

\chapter{Introduction} % Main chapter title

\label{ch:introduction} % Change X to a consecutive number; for referencing this chapter elsewhere, use \ref{ChapterX}

%----------------------------------------------------------------------------------------
%	SECTION 1
%----------------------------------------------------------------------------------------

\section{From 3D to 2D}

\section{Kinect and Surface Normal}

As a popular and affordable new type of depth sensor, Kinect, had attracted a great focus to computer vision research in the last decades. It simultaneously captured the grayscale or RGB image and depth map with a high resolution. The depth map can further convert to structured point clouds with known intrinsic calibration parameters, which can use in many applications.

%% why surface normal is important
Surface Normal is one of the most worthy pieces of information that can infer from point clouds, which applies in many practical applications, such as augmented reality and robotics. Some tasks like shading and surface reconstruction require normal as one of the inputs. However, due to the lack of accuracy of the sensors, the  surface normal inference from depth maps/point clouds has many challenges.

%-----------------------------------
%	SUBSECTION 1
%-----------------------------------
\section{Standard Methods}

@@

%-----------------------------------
%	SUBSECTION 2
%-----------------------------------

\section{Deep Learning based Method}
%% CNN based methods
Recently, deep learning based method \cite{yolov3}, \cite{efficientDet} achieved a great succeed for image processing. 
These network architectures use a batch of RGB/Grayscale images as input and usually employ for classification problems. Usually, the images are convoluted with a convolutional layer and downsampling with pooling layers. The outputs of the network consist of a single value to represent the index of the corresponding class \cite{efficientDet}, or with a set of values to represent the position of bounding boxes.\cite{yolov3}.

However, in many other vision tasks, like normal map inference, the output is demanded as the same shape as the input. Instead of predicting one or several classes for the whole input matrix, the class for each pixel requires for prediction. In this case, the traditional network architecture is not suitable anymore.

%----------------------------------------------------------------------------------------
%	SECTION 2
%----------------------------------------------------------------------------------------

\section{Challenges of Normal Inference}

@@

%% add noise image
\begin{figure}[th]
	\centering
	\includegraphics[width=.4\textwidth]{Figures/kinect-depth.png}
	\decoRule
	\caption{A captured depth map via infrared sensors. Pixels that far away represent by light colors, otherwise by dark colors. The black dots are the depths that failed to be detected.}
\label{fig:depth-map-with-noise}
\end{figure}

%% add noise image

\begin{figure}[th]
	\centering
	\includegraphics[width=.4\textwidth]{Figures/real-normal.png}
	\decoRule
	\caption{Semi-dense Normal Map calculated from depth map using a standard method}
\label{fig:standard-normal-inference}
\end{figure}

%%%%%%%%%%%%%%%%%% talk about the main work in this thesis  %%%%%%%%%%%%%%%%%%
\section{Main Works of this thesis}
In this thesis, we found a solution for the problems mentioned above and proposed a novel deep learning architecture for surface normal inference. A network named Albedo Gated Normal Inference Network(AlGaN) is proposed to infer normal given the corresponding depth map. The architecture of AlGaN involves a two-stage CNN. The first stage infers the normal map using point cloud as input. If the light source position and grayscale image can be provided further, the second stage infers the albedo altogether with the normals from the first stage. In addition, the loss function is based on least-square error and Lambertian reflection.

### 2022-06-19 paper/Chapters/Chapter02.tex
update paper

From considering neighborhoods in the same plane then using PCA for estimation to recently deep learning based methods, the task of surface normal inference is also been well studied in last 30 years.

>>>>

% Chapter Template

\chapter{Related Work} % Main chapter title

\label{ch:02} % Change X to a consecutive number; for referencing this chapter elsewhere, use \ref{ChapterX}

%----------------------------------------------------------------------------------------
%	SECTION 1
%----------------------------------------------------------------------------------------

From PCA for estimation to recently deep learning based methods, the task of surface normal inference is also been well studied in last several decades.
